SMT-Based Context-Bounded Model Checking for Embedded Systems: Challenges and Future Trends

### 2016-03-27 paper.tex
add new references

Novel verification algorithms for proving correctness of (a large set of) C programs, by mathematical induction, in a completely automatic way ({\it i.e.}, users do not need to provide the loop invariant) were recently proposed~\cite{Gadelha15,Beyer15,Brain15,Rocha15}. Additionally, \textit{k}-induction based verification was also applied to ensure that (restricted) C programs (1) do not contain violations related to data races~\cite{Donaldson10,Kinductor}, considering the Cell BE processor, and (2) do respect time constraints, which are specified during the system design phase~\cite{EenS03}. Apart from that, the \textit{k}-induction algorithm is also a well-established technique in hardware verification, where it is easily applied, due to the monolithic transition relation present in such designs~\cite{EenS03,Sheera00,GrosseLD09}.

@@

\textbf{(RP2)} The SMT-based BMC approach proposed by Cordeiro, Fischer, and Marques-Silva was further developed to verify correct lock acquisition ordering and the absence of deadlocks, data races, and atomicity violations in multi-threaded software based on POSIX and CUDA libraries~\cite{CordeiroF11,Pereira15}, considering monotonic partial-order reduction~\cite{KahlonWG09} and state-hashing techniques, in order to prune the state-space exploration~\cite{morse15}. Recent advances for verifying multi-threaded C programs have been proposed to speed up the verification time, which significantly prune the state-space exploration~\cite{Inverso14,civl15}; however, the class of concurrent programs ({\it e.g.}, CUDA, OpenCL, and MPI) that can be verified is still very limited. One possible research direction is to further extend BMC of multi-threaded C programs via Lazy Sequentialization~\cite{Inverso14}, in order to analyze unsatisfiability cores with the goal to remove redundant behaviour or to analyze interpolants to prove non-interference of context switches.

@@

%27
\bibitem{Donaldson10}
Donaldson A., Kroening D., R{\"{u}}mmer P.:
\newblock {\em {SCRATCH}: A Tool for Automatic Analysis of {DMA} Races.}
\newblock In: ACM Symposium on Principles and Practice of Parallel Programming. ACM, pp. 311--312, 2011.

%28
\bibitem{Kinductor}
Donaldson A., Haller L., Kroening D., R{\"{u}}mmer, P.:
\newblock {\em Software Verification using \textit{k}-Induction.}
\newblock In: International Conference on Static Analysis. LNCS 6887, pp. 351--368, 2011.

@@

%41
\bibitem{esbmc_controller}
Bessa I., Abreu R., Cordeiro L., Filho J.:
\newblock {\em {SMT-Based Bounded Model Checking of Fixed-Point Digital Controllers)}.}
\newblock In: Annual Conference of the Industrial Electronics Society, pp. 295--301, 2014.

%42
\bibitem{esbmc_filter}
Abreu R., Cordeiro L., Filho E.:
\newblock {\em {Verifying Fixed-Point Digital Filters using SMT-Based Bounded Model Checking}.}
\newblock In: XXXI Brazilian Symposium on Telecommunications, 2013.
\newblock http://dx.doi.org/10.14209/sbrt.2013.57

%43
\bibitem{JMorse15}
Morse J., Cordeiro L., Nicole D., Fischer B.:
\newblock {\em {Model Checking LTL Properties over ANSI-C Programs with Bounded Traces.}} 
\newblock In: Software and System Modeling 14(1): pp. 65--81, 2015.

%44
\bibitem{Bessa16}
Bessa I., Ismail H., Cordeiro L., Chaves Filho J.:
\newblock {\em { Verification of Fixed-Point Digital Controllers Using Direct and Delta Forms Realizations.}} 
\newblock In: Design Automation for Embedded Systems (to appear), 2016.

%45
\bibitem{MorseCNF13}
Morse J., Cordeiro L., Nicole D., Fischer B.:
\newblock {\em Handling unbounded loops with {ESBMC} 1.20.}
\newblock In: Tools and Algorithms for the Construction and Analysis of
  Systems. LNCS 7795, Springer Berlin Heidelberg, pp. 619--622, 2013.

%46
\bibitem{MorseRCN014}
Morse J., Ramalho M., Cordeiro L., Nicole D., Fischer B.:
\newblock {\em {ESBMC} 1.22.}
\newblock In: Tools and Algorithms for the Construction and Analysis of
  Systems. LNCS 8413, Springer Berlin Heidelberg, pp. 405--407, 2014.

%47
\bibitem{KahlonWG09}
Kahlon V., Wang C., Gupta A.:
\newblock {\em{Monotonic Partial Order Reduction: An Optimal Symbolic Partial Order Reduction Technique}}.
\newblock In: International Conference on Computer-Aided Verification, LNCS 5643, pp. 398--413, 2009.

%48
\bibitem{Alves15}
Alves E. , Cordeiro L., Lima Filho E.:
\newblock {\em{ Fault Localization in Multi-Threaded C Programs using Bounded Model Checking}}. 
\newblock In: Brazilian Symposium on Computing Systems Engineering, pp. 96-101, 2015.

%49
\bibitem{BeyerW15}
Beyer D., Dangl M., Dietsch D., Heizmann M., Stahlbauer A.:
\newblock {\em{ Witness validation and stepwise testification across software verifiers}}. 
\newblock In: ESEC/SIGSOFT Foundations of Software Engineering, pp. 721--733, 2015.

%50
\bibitem{RochaIFM12}
Rocha H., Barreto R., Cordeiro L., Dias Neto A.:
\newblock {\em{ Understanding Programming Bugs in ANSI-C Software Using Bounded Model Checking Counter-Examples}}. 
\newblock In: International Conference on Integrated Formal Methods, LNCS 7321, pp. 128-142, 2012.

>>>>

Novel verification algorithms for proving correctness of (a large set of) C programs, by mathematical induction, in a completely automatic way ({\it i.e.}, users do not need to provide the loop invariant) were recently proposed~\cite{Gadelha15,Beyer15,Brain15,Rocha15,Kinductor}. Additionally, \textit{k}-induction based verification was also applied to ensure that (restricted) C programs (1) do not contain violations related to data races~\cite{Donaldson10}, considering the Cell BE processor, and (2) do respect time constraints, which are specified during the system design phase~\cite{EenS03}. Apart from that, the \textit{k}-induction algorithm is also a well-established technique in hardware verification, where it is easily applied, due to the monolithic transition relation present in such designs~\cite{EenS03,Sheera00,GrosseLD09}.

@@

\textbf{(RP2)} The SMT-based BMC approach proposed by Cordeiro, Fischer, and Marques-Silva was further developed to verify correct lock acquisition ordering and the absence of deadlocks, data races, and atomicity violations in multi-threaded software based on POSIX and CUDA libraries~\cite{CordeiroF11,Pereira15}, considering monotonic partial-order reduction~\cite{KahlonWG09} and state-hashing techniques, in order to prune the state-space exploration~\cite{morse15}. Recent advances for verifying multi-threaded C programs have been proposed to speed up the verification time, which significantly prune the state-space exploration~\cite{Inverso14,civl15}; however, the class of concurrent programs ({\it e.g.}, CUDA, OpenCL, and MPI) that can be verified is still very limited. One possible research direction is to further extend BMC of multi-threaded C programs via Lazy Sequentialization~\cite{Inverso14}, in order to analyze unsatisfiability cores~\cite{Grumberg05} with the goal to remove redundant behaviour or to analyze interpolants~\cite{McMillan11} to prove non-interference of context switches.

@@

%27
\bibitem{Kinductor}
Donaldson A., Haller L., Kroening D., R{\"{u}}mmer, P.:
\newblock {\em Software Verification using \textit{k}-Induction.}
\newblock In: International Symposium on Static Analysis. LNCS 6887, pp. 351--368, 2011.

%28
\bibitem{Donaldson10}
Donaldson A., Kroening D., R{\"{u}}mmer P.:
\newblock {\em {SCRATCH}: A Tool for Automatic Analysis of {DMA} Races.}
\newblock In: ACM Symposium on Principles and Practice of Parallel Programming. ACM, pp. 311--312, 2011.

@@

%41
\bibitem{Grumberg05}
Grumberg O., Lerda F., Strichman O., Theobald M.:
\newblock {\em { Proof-guided underapproximation-widening for multi-process systems.}} 
\newblock In: Symposium on Principles of Programming Languages, pp. 122--131, 2005.

%42
\bibitem{McMillan11}
K.~McMillan:
\newblock {\em {Widening and Interpolation.}} 
\newblock In: International Symposium on Static Analysis, LCNS 6887, pp. 1, 2011.

%43
\bibitem{esbmc_controller}
Bessa I., Abreu R., Cordeiro L., Filho J.:
\newblock {\em {SMT-Based Bounded Model Checking of Fixed-Point Digital Controllers)}.}
\newblock In: Annual Conference of the Industrial Electronics Society, pp. 295--301, 2014.

%44
\bibitem{esbmc_filter}
Abreu R., Cordeiro L., Filho E.:
\newblock {\em {Verifying Fixed-Point Digital Filters using SMT-Based Bounded Model Checking}.}
\newblock In: XXXI Brazilian Symposium on Telecommunications, 2013.
\newblock http://dx.doi.org/10.14209/sbrt.2013.57

%45
\bibitem{JMorse15}
Morse J., Cordeiro L., Nicole D., Fischer B.:
\newblock {\em {Model Checking LTL Properties over ANSI-C Programs with Bounded Traces.}} 
\newblock In: Software and System Modeling 14(1): pp. 65--81, 2015.

%46
\bibitem{Bessa16}
Bessa I., Ismail H., Cordeiro L., Chaves Filho J.:
\newblock {\em { Verification of Fixed-Point Digital Controllers Using Direct and Delta Forms Realizations.}} 
\newblock In: Design Automation for Embedded Systems (to appear), 2016.

%47
\bibitem{MorseCNF13}
Morse J., Cordeiro L., Nicole D., Fischer B.:
\newblock {\em Handling unbounded loops with {ESBMC} 1.20.}
\newblock In: Tools and Algorithms for the Construction and Analysis of
  Systems. LNCS 7795, Springer Berlin Heidelberg, pp. 619--622, 2013.

%48
\bibitem{MorseRCN014}
Morse J., Ramalho M., Cordeiro L., Nicole D., Fischer B.:
\newblock {\em {ESBMC} 1.22.}
\newblock In: Tools and Algorithms for the Construction and Analysis of
  Systems. LNCS 8413, Springer Berlin Heidelberg, pp. 405--407, 2014.

%49
\bibitem{KahlonWG09}
Kahlon V., Wang C., Gupta A.:
\newblock {\em{Monotonic Partial Order Reduction: An Optimal Symbolic Partial Order Reduction Technique}}.
\newblock In: International Conference on Computer-Aided Verification, LNCS 5643, pp. 398--413, 2009.

%50
\bibitem{Alves15}
Alves E. , Cordeiro L., Lima Filho E.:
\newblock {\em{ Fault Localization in Multi-Threaded C Programs using Bounded Model Checking}}. 
\newblock In: Brazilian Symposium on Computing Systems Engineering, pp. 96-101, 2015.

%51
\bibitem{BeyerW15}
Beyer D., Dangl M., Dietsch D., Heizmann M., Stahlbauer A.:
\newblock {\em{ Witness validation and stepwise testification across software verifiers}}. 
\newblock In: ESEC/SIGSOFT Foundations of Software Engineering, pp. 721--733, 2015.

%52
\bibitem{RochaIFM12}
Rocha H., Barreto R., Cordeiro L., Dias Neto A.:
\newblock {\em{ Understanding Programming Bugs in ANSI-C Software Using Bounded Model Checking Counter-Examples}}. 
\newblock In: International Conference on Integrated Formal Methods, LNCS 7321, pp. 128-142, 2012.
